\begin{problem}{Dice Game}{standard input}{standard output}{dice}

Gunnar and Emma play a lot of board games at home, so they own many dice that are not normal 6-sided
dice. For example they own a die that has 10 sides with numbers 47, 48, ..., 56 on it.\\

There has been a big storm in Stockholm, so Gunnar and Emma have been stuck at home without
electricity for a couple of hours. They have finished playing all the games they have, so they came
up with a new one. Each player has 2 dice which he or she rolls. The player with a bigger sum wins.
If both sums are the same, the game ends in a tie.\\

Your task is: Given the description of Gunnar’s and Emma’s dice, which player has higher chances of
winning?\\

All of their dice have the following property: each die contains numbers $a, a + 1, . . . , b$,
where $a$ and $b$ are the lowest and highest numbers respectively on the die.\\

Each number appears exactly on one side, so the die has $b - a + 1$ sides.

\InputFile

The first line contains four integers $a_1, b_1, a_2, b_2$ that describe Gunnar's dice.
Dice number $i$ contains numbers $a_i, a_i + 1, . . . , b_i$ on its sides. You may assume
that $1 \leq a_i \leq b_i \leq 100$. You can further assume that each die has at least four sides,
so $a_i + 3 \leq b_i$.\\

The second line contains the description of Emma's dice in the same format.\\

\OutputFile

Output the name of the player that has higher probability of winning. Output ``Tie'' if both players
have same probability of winning.\\

\Example

\begin{example}
\exmp{
1 4 1 4
1 6 1 6
}{
Emma
}%
\exmp{
1 8 1 8
1 10 2 5
}{
Tie
}%
\exmp{
2 5 2 7
1 5 2 5
}{
Gunnar
}%
\end{example}

\end{problem}
